Online reprocessing simulation for thorium-fueled molten salt breeder reactor

### 2017-07-07 msbr_reproc.tex
hard wrapped all lines for better diffing

\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
The thermal spectrum \gls{MSR} is an advanced type of reactor consist of constantly circulating liquid fuel (i.e., mixture of $LiF-BeF_2-ThF_4-UF_4$ or $LiF-BeF_2-ZrF_4-UF_4$) which works also as a coolant, and the reactor graphite as moderator. This fuel form leads to immediate advantages over traditional, solid-fueled, reactors. The molten-salt carrier salt with dissolved in it fissile and/or fertile material allows to use online refuelling and reprocessing, which means \gls{MSR}s can operate years without shutdown, achieve maximum fuel utilization, and outstanding neutron economy \cite{leblanc_molten_2010}. Moreover, this type of fuel does not need fabrication and could be transported from enrichment plant to \gls{NPP} in form of uranium hexafluoride ($UF_6$), so \gls{MSR}s are also beneficial with regards to economics. Additionally, it has high level of inherent safety due to strong negative temeperature coefficient of reactivity, near-atmospheric pressure in the primary loop, stable coolant, passive decay heat cooling, and small excess reactivity \cite{elsheikh_safety_2013}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\captionsetup[table]{
  labelsep = newline,
  name = TABLE, 
  justification=justified,
  singlelinecheck=false,%%%%%%% a single line is centered by default
  labelsep=colon,%%%%%%
  skip = \medskipamount}
\begin{table}[h!]
%\centering
\begin{tabular}{p{0.46\linewidth} p{0.50\linewidth}} \toprule
Thermal capacity of reactor           & 2250 MW(t)
\\ \midrule
%Net electrical output                 & 1000 MW(e) 
%\\ \midrule
%Net thermal efficiency        & 44.4\%
%\\ \midrule
Volume fraction of salt in central core zone     & 0.132
\\ \midrule
Volume fraction of salt in outer core zone       & 0.37
\\ \midrule
Fuel-salt inventory (Zone I)                  & 8.2 m$^3$	
\\ \midrule
Fuel-salt inventory (Zone II)                 & 10.8 m$^3$	
\\ \midrule
Fuel salt components                  & LiF-BeF$_2$-ThF$_4$-$^{233}$UF$_4$-$^{239}$PuF$_3$	
\\ \midrule
Fuel salt composition                 & 71.767-16-12-0.232-0.0006 mole\%
\\
\bottomrule
\end{tabular}
  \caption{Summary of principal data for MSBR.}
  \label{tab:data}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

The analysis of the fuel salt composition variation gives clearer information about equilibrium core state. Figure~\ref{fig:compos} shows the normalized number density of important isotopes that have strong influence on the core neutronics at the beginning of each depletion time interval. The number density of protactinium is very low (less than $10^{16}$1/cm$^3$) but some small amount of it produced during 3-days reprocessing step. It can be seen that the the multiplication factor reaches the equilibrium state at about 950  days. Figure~\ref{fig:rates} represents the rates of materials in online reprocessing flows during 4 years of depletion calculations. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\captionsetup[table]{
%  labelsep = newline,
%  name = TABLE, 
%  justification=justified,
%  singlelinecheck=false,%%%%%%% a single line is centered by default
%  labelsep=colon,%%%%%%
%  skip = \medskipamount}
%\begin{table}[h!]
%\centering
%\begin{tabular}{p{0.25\linewidth} p{0.3\linewidth} p{0.3\linewidth}} \toprule
%      Isotope & First 400 days     & After 400 days          
%\\ \midrule
%$^{232}$Th  & 3.704$\times10^{12}$ & 3.086$\times10^{12}$
%\\ \midrule
%$^{233}$Pa  & 3.704$\times10^{12}$ & 3.086$\times10^{12}$
%\\ \midrule
%$^{233}$U  & $1.05134\pm0.00116$ & $1.00736$
%\\
%\bottomrule
%\end{tabular}
%  \caption{Materials flows rates during \gls{MSBR} online reprocessing [1/s*cm$^3$].}
%  \label{tab:rates}
%\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[hb] % replace 't' with 'b' to force it to be on the bottom
  \centering
  \vspace{-0.8em}
  \includegraphics[width=1.03\linewidth]{rates_fuel.png}
  \caption{Materials flows rates during online reprocessing.}
  \label{fig:rates}
  \vspace{-0.8em}
\end{figure}
From the graph below we can see that to keep reactor critical higher $^{233}$U flow rate required for first 400 days of operation and after that much smaller uranium-233 flow rate from the protactinium decay tank needed. The $^{232}$Th rate slightly decreases over 4 years of operation due to other than $^{233}$U fissile materials accumulation.

>>>>

\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
The thermal spectrum \gls{MSR} is an advanced type of reactor consisting of 
constantly circulating liquid fuel (i.e., mixture of $LiF-BeF_2-ThF_4-UF_4$ or 
$LiF-BeF_2-ZrF_4-UF_4$) which also works as a coolant, and the reactor graphite 
as moderator. This fuel form leads to immediate advantages over traditional, 
solid-fueled, reactors. The molten-salt carrier salt with dissolved in it 
fissile and/or fertile material allows to use online refuelling and 
reprocessing, which means \gls{MSR}s can operate years without shutdown, 
achieve maximum fuel utilization, and outstanding neutron economy 
\cite{leblanc_molten_2010}. Moreover, this type of fuel does not need 
fabrication and could be transported from enrichment plant to \gls{NPP} in form 
of uranium hexafluoride ($UF_6$), so \gls{MSR}s are also beneficial with 
regards to economics. Additionally, it has high level of inherent safety due to 
strong negative temeperature coefficient of reactivity, near-atmospheric 
pressure in the primary loop, stable coolant, passive decay heat cooling, and 
small excess reactivity \cite{elsheikh_safety_2013}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\captionsetup[table]{
        labelsep = newline,
        name = TABLE, justification=justified,
        singlelinecheck=false,%%%%%%% a single line is centered by default
        labelsep=colon,%%%%%%
skip = \medskipamount}
\begin{table}[h!]
        %\centering
        \begin{tabular}{p{0.46\linewidth} p{0.50\linewidth}} \toprule
                Thermal capacity of reactor           & 2250 MW(t)
                \\ \midrule
                %Net electrical output                 & 1000 MW(e) \\ \midrule
                %Net thermal efficiency        & 44.4\%
                %\\ \midrule
                Volume fraction of salt in central core zone     & 0.132
                \\ \midrule
                Volume fraction of salt in outer core zone       & 0.37
                \\ \midrule
                Fuel-salt inventory (Zone I)                  & 8.2 m$^3$	
                \\ \midrule
                Fuel-salt inventory (Zone II)                 & 10.8 m$^3$	
                \\ \midrule
                Fuel salt components                  & 
                LiF-BeF$_2$-ThF$_4$-$^{233}$UF$_4$-$^{239}$PuF$_3$	\\ 
                \midrule
                Fuel salt composition                 & 
                71.767-16-12-0.232-0.0006 mole\%
                \\
                \bottomrule
        \end{tabular}
        \caption{Summary of principal data for MSBR.}
        \label{tab:data}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

The analysis of the fuel salt composition variation gives clearer information 
about equilibrium core state. Figure~\ref{fig:compos} shows the normalized 
number density of important isotopes that have strong influence on the core 
neutronics at the beginning of each depletion time interval. The number density 
of protactinium is very low (less than $10^{16}$1/cm$^3$) but some small amount 
of it produced during 3-days reprocessing step. It can be seen that the the 
multiplication factor reaches the equilibrium state at about 950  days. 
Figure~\ref{fig:rates} represents the rates of materials in online reprocessing 
flows during 4 years of depletion calculations. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\captionsetup[table]{
%  labelsep = newline,
%  name = TABLE, justification=justified,
%  singlelinecheck=false,%%%%%%% a single line is centered by default
%  labelsep=colon,%%%%%%
%  skip = \medskipamount}
%\begin{table}[h!]
%\centering
%\begin{tabular}{p{0.25\linewidth} p{0.3\linewidth} p{0.3\linewidth}} \toprule
%      Isotope & First 400 days     & After 400 days          
%\\ \midrule
%$^{232}$Th  & 3.704$\times10^{12}$ & 3.086$\times10^{12}$
%\\ \midrule
%$^{233}$Pa  & 3.704$\times10^{12}$ & 3.086$\times10^{12}$
%\\ \midrule
%$^{233}$U  & $1.05134\pm0.00116$ & $1.00736$
%\\
%\bottomrule
%\end{tabular}
%  \caption{Materials flows rates during \gls{MSBR} online reprocessing 
%  [1/s*cm$^3$].}
%  \label{tab:rates}
%\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[hb] % replace 't' with 'b' to force it to be on the bottom
        \centering
        \vspace{-0.8em}
        \includegraphics[width=1.03\linewidth]{rates_fuel.png}
        \caption{Materials flows rates during online reprocessing.}
        \label{fig:rates}
        \vspace{-0.8em}
\end{figure}
From the graph below we can see that to keep reactor critical higher $^{233}$U 
flow rate required for first 400 days of operation and after that much smaller 
uranium-233 flow rate from the protactinium decay tank needed. The $^{232}$Th 
rate slightly decreases over 4 years of operation due to other than $^{233}$U 
fissile materials accumulation.
